---
title: "README"
author: "Bob Rudis"
date: January 09, 2015
output:
  md_document:
    variant: markdown_github
---

localgeo is a package that coverts a US City+State to lon/lat. This is a ridiculously 
small package and is really just a function interface over the `cities.rda` file in the
`data` directory. So, just grab that if you want to wrap your own work around it. 

It was made in response to http://stackoverflow.com/a/27868207/1457051 since there's no reason to waste bandwidth or cycles on an internet API when you can have the data locally.

The following functions are implemented:

- `geocode` : converts US city/states to lon/lat

### News

- Version 0.1 released

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/localgeo")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(localgeo)

# current verison
packageVersion("localgeo")

print(geocode("Eliot", "ME"))

print(geocode(city=c("Houston", "Pittsburgh"),
              state=c("TX", "PA")))


```

### Test Results

```{r}
library(localgeo)
library(testthat)

date()

test_dir("tests/")
```

